Gamification Effectiveness on Education

### 2024-04-17 paper/paper.qmd
fixed table1 and finish the data section

The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control(N=76), Educational game(N=75), Gamification Plugin(N=77), Social networking website(N=75), Social gamified networking website(N=76). The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with hybrid learning. This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases. There is an assignment for each of these four concepts which focus on testing practical skills. While, the final examination is cumulative and focus on testing conceptual knowledge.

Students have lecture every two weeks and must work independently rest of the work to learn then material. Supplementary learning material was provided such as videos and communication tools in learning material platform.

The control group just use what was mention above. Educational game used was called Ribbonhero offered by Microsoft as as free download to download Software, and player plays as virtual character Clippy and must overcome six challenges with increasing difficulty. Gamification plugin (@fig-Gamification-plugin) is integrated in the institutional management system where there are challenges, trophies/badges and a leader board. Social Networking website was run on a open source engine, Elgg (@fig-social_network) and it functions very similar to social media where students can share their thoughts, make friends and discuss the material in class. Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(@fig-social_gamification). A summary of the groups features and potential benefits(@tbl-summary-group). The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.

@@

htmltools::includeHTML(file.path(here::here(),"other/tables/table1.html"))
```

## Data Cleaning Procedure

@@

@@

## Good example of Gamification

## Student's opinon about it

>>>>

The original study used 379 undergraduates for their experiments and there were randomly assigned into 5 groups Control(N=76), Educational game(N=75), Gamification Plugin(N=77), Social networking website(N=75), Social gamified networking website(N=76). The experiment was carried out on 10-week first year undergraduate class called ‘Qualification for ICT Users’ with blended learning. This course is an introduction to basic computing concepts such as word processing, spreadsheets, presentations and databases.

In this experiment, before applying the corresponding learning methods, the students take a pretest, which occurs in week 1. And through week 2-9, depending on the group the student was assigned they learn using that specific method. During those weeks, they were assigned four assignments(aka post tests) on week 3, 5, 7 and 9. In addition, these assignments are on word processing, spreadsheets, presentations and databases, which tests students on practical skills. Finally, there is cumulative final exam and tests students on conceptual knowledge.

All groups had students have lecture every two weeks and must work independently rest of the work to learn then material using their respective method. In addition, Supplementary learning material was provided such as videos and communication tools in learning material platform. The control group just use traditional e-learning approach that was mention above. Educational game used was called Ribbonhero offered by Microsoft as as free download to download Software, and player plays as virtual character Clippy and must overcome six challenges with increasing difficulty. Gamification plugin (@fig-Gamification-plugin) is integrated in the institutional management system where there are challenges, trophies/badges and a leader board. Social Networking website was run on a open source engine, Elgg (@fig-social_network) and it functions very similar to social media where students can share their thoughts, make friends and discuss the material in class. Social gamified networking website use the same engine as the previous group and having similar features to Gamification plugin(@fig-social_gamification). A summary of the groups features and potential benefits(@tbl-summary-group). The study highlights that the educational game is not necessarily aligned with the learning goals, while the gamification used in this study was.

@@

knitr::include_graphics(file.path(here::here(),"other/tables/table1.jpg"))
```

## Variables of Interest and Data Cleaning Procedure
The variables used in this study are Group, Gender, pretest and post test for Word Processing, Spreadsheets, Presentation, Databases and FinalExamination. Pretest, post test and FinalExamination use the measurement of a grade, which is from 0 - 100%.

@@

## Is Gamification effective? Does it have pontential to change the educational system?

@@

## Student's input
